Predicting Covid Data

### 2022-12-05 main.rmd
Combined introduction and formatted the plots

## Introduction : Ciufolini and Paolozzi's Study

* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
  * They have then use the function to approximate the number of cumulative positive cases in Italy
  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

## Cont.

* The number of cumulative diagnosed positive cases and fatalities in China approximates a gauss error function: $a+b*erf(c*x-d)$.
* Predicted the potential number of cases in Italy.
* Predicted the day in which the peak of the number of daily cases in Italy occurs.

@@

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases), color = "red") +
  labs(x = "Date", y = "China cumulative number of cases")
positive
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths), color = "red") +
  labs(x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases), color = "red") +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1) +
  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]), color="blue")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2) +
  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
```

>>>>

## Ciufolini and Paolozzi's Study

* The time evolution of the number of cumulative diagnosed positive cases and fatalities in China approximates the distribution of a gauss error function: $a+b*erf(c*x-d)$.
* Performed the function on Italy data to predict the potential number of cases.
* Performed the Monte Carlo Simulations to predict the day in which the peak of the number of daily cases in Italy occurs.

@@

# recreate plots
positive <- ggplot(data = china) +
  geom_point(aes(x = date, y = total_cases)) +
  labs(x = "Date", y = "China cumulative number of cases")
positive
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold", out.width="50%"}
ggplot(data = china) +
  geom_point(aes(x = date, y = total_deaths)) +
  labs(x = "Date", y = "China cumulative number of fatalities") +
  ylim(0,5000)
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases)) +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="#d33636", size=1.5) + 
  geom_vline(xintercept = peak1, color="#d33636", size=1.5, linetype="dashed")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths)) +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="#1b95ff", size=1.5) + 
  geom_vline(xintercept = peak2, color="#1b95ff", size=1.5, linetype="dashed")
```
